Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2013-03-01 doc/response.txt

1. The paper does not describe the resolution of the convergence maps
from the simulation.  The only number quoted is 30 arcseconds, which
(hopefully!) is not the resolution of the maps.  For example, the
convergence power spectrum peaks on arcminute scales, even neglecting
baryonic effects which only increase small-scale power. Therefore a 30
arcsecond resolution would be woefully inadequate for the purposes of
this study.  The authors should describe their simulations in more
detail, and discuss what fraction of the convergence power is
unresolved by their simulations.

# We have updated section 3.1 to state the resolution of our simulations,
and explain why it should be sufficient for our purposes.

2. My main concern about this work is that the halo occupation
distribution is assumed to be known.  As mentioned in the final
paragraph of the paper, this is a severe limitation which makes it
difficult to assess the validity of the claimed results. In reality,
uncertainties in the HOD will lead to uncertainties in the
reconstruction, and the authors should provide some estimate of these
errors.  For example, the authors could provide an example in which
the "wrong" HOD is assumed, and then compute the resulting errors in
the convergence reconstruction.  One easy example of this could be to
use the stellar masses from the Millennium catalog, which were
discarded in favor of the model of Behroozi et al.

# We agree that this is an important systematic, but we have not implemented the
suggested test. Swapping Behroozi stellar masses for the Millenium catalogue's
stellar masses is too a extreme a change to be realistic - one wants to test the effect of using a wrong HOD, where both models within the observational limits, in light of this we have applied to the Moster et al. (????) stell mass-halo mass relation, to generate 'true' stellar masses and reconstructed these using the Behroozi relation. The results of this investigation have been included in a new section 8.

### 2013-03-01 doc/paper-lcr.tex
added section on SM-HM relation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Systematic Errors due to using an incorrect Stellar Mass--Halo Mass Relation}
\label{sec:biases}

\begin{figure*}
\includegraphics[width=\textwidth]{figs/SHAMbias.eps}
\caption{Systematic bias in $\kappax$ due to reconstructing lines of sight with the wrong stellar mass--halo mass relation. The real stellar masses were created using the relation of \citet{MosterEtal2010}, but the reconstruction and calibration assumes the relation of \citet{BehrooziEtal2010}.  These plots
show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
deviations from zero represent biases. The solid, dashed and dotted lines
correspond to combinations of  20, 5 and 2 sightlines respectively. Black
lines show the results \infered from photometry alone, whilst red lines show
the results  from the same targeted spectroscopy campaign described in 
\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
sightlines selected in different ways. Left: randomly selected lines of
sight.  Centre: sightlines randomly selected from the 33\% of lines whose
P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
with external shear of 0.05 or greater.}
\label{fig:SHAMbias}
\end{figure*}

\new{
Throughout this work we have assumed that the universe's halos are populated with galaxies whose stellar masses are determined purely by the \citet{BehrooziEtal2010} Stellar Mass--Halo Mass relation. The real universe is unlikely to follow this relation perfectly; the result is that an ensemble of real lines of sight will differ from the ensemble of calibration lines of sight, potentially introducing a systematic error to the reconstructed convergence.

We test the potential size of this systematic error by using the \citet{BehrooziEtal2010} relation to generate the stellar masses of our calibration lines of sight, but the Stellar Mass--Halo Mass relation of \citet{MosterEtal2010} for the 'real' lines of sight that are reconstructed.

For halos masses of $\sim 10^{12} \Msun$ both stellar mass--halo mass relations estimate a stellar mass of $\sim 10^{10.5} \Msun$, but for halos more massive that this the stellar masses generated from the Moster relation are systematically higher than those generated from the Behroozi relation. At halo masses of $\sim 10^{14} \Msun$ the best fit stellar masses differ by $\sim 0.25$ dex.

Applying our Behroozi--based reconstruction to lines of sight with Moster stellar masses results in systematically overestimating $\kappax$. In \Fref{fig:SHAMbias} we show the resulting bias on the inferred $\kappax$ after combining several lines of sight. With a purely photometric reconstruction there is a typical systematic bias of $\sim 0.025$ on the reconstructed convergence, although it can be shrunk to $\sim 0.01$ if only the low $\kappax$ lines of sight are used, however for the high shear lines of sight the bias is $\sim 0.04$. It is not suprising that the low $\kappax$ lines of sight are least affected by changes in the stellar mass--halo mass relation. Low $\kappax$ lines of sight are relatively empty hence their $\kappah$ values are small and do not change significantly with stellar mass--halo mass relation. The high shear lines of sight have significantly overestimated $\kappax$ since they tend to lie close to massive halos. This is the regime where the Moster and Behroozi relations are most different.

Despite the systematic errors the photometric reconstruction is still sufficient to choose the best lines of sight for spectroscopic follow-up. With targetted spectroscopy the systematic error decreases to $\sim 0.014$ for the ensemble, $\sim 0.005$ for the low kappa sample and $\sim 0.018$ for the high shear sample. 
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
